% cv-us.tex
% $Id: cv-us.tex,v 1.28 2006/12/12 22:53:52 jrblevin Exp $
%
% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2006 Jason Blevins
% Copyright (C) 2007 Leonardfo Franchi
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents, however, I do ask that you
% please leave this notice and the above URL in the source code if you
% choose to redistribute this file.
%
% Jason R. Blevins <jrblevin@sdf.lonestar.org>
% http://jrblevin.freeshell.org
% Durham, December 12, 2006
%
%%---------------------------------------------------------------------------%
%
% Notes:
%
% * Don't forget to change `pdfauthor' and `keywords' in the \hypersetup
%   section below.
%
% * To create a new page use: \newpage \opening
%
% * res.cls includes an \address{} command which can be used up to twice,
%   but my address is too long for the format it uses.
%
% * Alternate documentclass statement to put headings in margin:
%   \documentclass[margin,line,11pt,final]{res}
%
% * Can divide publication/presentation list into subsections by year:
%   \section{\bf\small\hspace{8mm}2006}
%
%%----------------------------------------------------------------------------%

\documentclass[overlapped,line,letterpaper]{res}

\usepackage{ifpdf}



\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}


\hypersetup{
  letterpaper,
  colorlinks,
  urlcolor=black,
  pdfpagemode=none,
  pdftitle={Curriculum Vitae},
  pdfauthor={Leonardo Franchi},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={computer science artificial intelligence robotics kde open source amarok}
}

%margins
\usepackage[top=2cm,left=1.2cm,right=3.1cm,bottom=1.5cm]{geometry}

%%===========================================================================%%

\begin{document}

% no page number
\thispagestyle{empty}
% smaller right margin
\resumewidth=3.0in
\sectionskip 1.0em

%my fonts


%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0.0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

%---------------------------------------------------------------------------

\name{Leonardo Franchi}

\begin{resume}


\begin{ncolumn}{4}
  113 Prospect St, Apt 1 &  & (512) 775 5637 \\
  Somerville, MA 02143  &   &  https://github.com/lfranchi & {lfranchi@kde.org}
\end{ncolumn}

%---------------------------------------------------------------------------

\section{\bf Education}

% \begin{format}
% \line{l}
% 
% \end{format}

Tufts University, Medford, MA.\newline
B.A. in Computer Science and Philosophy, cum laude.  2010\newline

%---------------------------------------------------------------------------


\section{\bf Work Experience}

\begin{format}
\employer{l}\location{r}\\
\title{l}\dates{r}\\
\body\\
\end{format}

\employer{\textbf{Humbug, Inc}}
\location{Cambridge, MA}
\dates{Jan 2013--Present}
\title{Software Engineer}
\begin{position}
\textbullet \space Engineer at early-stage startup, involved in all aspects of development. \\
\textbullet \space Developed, designed and architected backend Python services and frontend Javascript.
\end{position}

\employer{\textbf{Hacker School}}
\location{Brooklyn, NY}
\dates{Oct 2012--Dec 2012}
\title{Hacker}
\begin{position}
\textbullet \space Built a networked daemon in Clojure that replicates a SQL database amongst peers.\\
\textbullet \space Implemented a Software Transactional Memory system in Python for Clojure-Py.\\
\textbullet \space Contributed to a distributed fault-tolerant Go project for running arbitrary services in a reliable manner. \\
\textbullet \space Contributed to Droplet, a Clojure DSL implementing the Bloom$^L$ language. \\
\textbullet \space Developed commutative replicated data types (CRDTs) as well as examples for the droplet project.
\end{position}

\employer{\textbf{Tomahawk Player}}
\location{Cambridge, MA}
\dates{June 2010--Present}
\title{Software Developer}
\begin{position}
\textbullet \space Developer of cross-platform open-source social media player Tomahawk. \\
\textbullet \space Wrote C++, Objective-C, Javascript to provide a seamless music experience that encompasses the web.
\end{position}

\employer{\textbf{KDAB (USA) LLC.}}
\location{Cambridge, MA}
\title{Software Engineer}
\dates{Sept 2009---December 2012}
\begin{position}
\textbullet \space Cross-platform C++ development with the Qt framework.\\
\textbullet \space Developed touch-screen and low-resolution UIs for touch screen and embedded devices.\\
\textbullet \space Bugfixing and feature development for large and small  Windows, OS X, and Linux applications. \end{position}

\employer{\textbf{Mitsubishi Electric Research Laboratories}}
\location{Cambridge, MA}
\title{Intern, Speech Group}
\dates{May-August, 2008 \& 2009}
\begin{position}
\textbullet \space Developed Java and C applications for the Android platform. \\
\textbullet \space Ported speech recognition engine in C to Android with JNI. \\
\textbullet \space Ported existing Windows-specific code to Linux and ARM/Embedded systems. \\
\textbullet \space Investigated information retrieval systems and their applications to broad cross-domain speech recognition. \\
\textbullet \space Generated comparisons of speech recognition backends over word- and particle-based speech synthesis.
\end{position}

\employer{\textbf{Amarok}}
\location{Medford, MA}
\dates{June 2005--July 2010}
\title{Software Developer}
\begin{position}
\textbullet \space Developer of leading open-source audio player Amarok for the GNU/Linux and Mac OS X operating systems. \\
\textbullet \space Developed dynamic graphical user interfaces, scripting interfaces, web service integration, and other features and bugfixes.
\end{position}

\employer{\textbf{Google Summer of Code}}
\location{Medford, MA}
\dates{May 2007--August 2009}
\title{Student, Mentor, Administrator}
\begin{position}
\textbullet \space Managed and organized KDE Project's 50 GSoC students and mentors.\\
\textbullet \space Managed and tracked progress of mentee in the GSoC program. Assisted and guided student's development.\\
\textbullet \space Designed innovative ways of using SVG-themed applets to visually represent data. \\
\textbullet \space Extended and adapted a flexible client/server model in order to provide a reliable and reusable system for managing visually appealing applets.
\end{position}

\employer{\textbf{Information Technology, Tufts University}}
\location{Medford, MA}
\title{Student RCC}
\dates{August 2007--May 2008}
\begin{position}
\textbullet \space Dealt with user support as well as troubleshooting, repairing, and restoring of users' systems as a member of the front-line support staff for Tufts University Information Technology.
\end{position}

\begin{format}
\employer{l}\location{r}\\
\title{l}\dates{r}\\
\body\\
\end{format}

\section{\bf Talks}

\begin{format}
\employer{l}\location{r}\\
\title{l}\dates{r}\\
\body\\
\end{format}

\employer{\textbf{Akademy 2010}}
\location{Tampere, Finland}
\dates{July, 2010}
\title{Blurring the Boundaries of Music}
\begin{position}
\textbullet \space Announcing Tomahawk, a media player designed for our social music day and age. 
\end{position}

\employer{\textbf{Camp KDE 2010}}
\location{San Diego, California}
\dates{January, 2010}
\title{Making Your Media Player Intelligent}
\begin{position}\textbullet \space Media players have failed to evolve and keep up with new innovation in the music sphere.
\end{position}

\employer{\textbf{Camp KDE 2009}}
\location{Negril, Jamaica}
\dates{January, 2009}
\title{Integrating libplasma in Desktop Applications}
\begin{position}\textbullet \space An account of my experience integrating libplasma in the Amarok media player. \\
\textbullet \space Pitfalls of using the plasma framework for displaying dynamic content in your standalone application.
\end{position}

% \section{\bf Research Experience}

\begin{format}
\employer{l}\location{r}\\
\title{l}\dates{r}\\
\body\\
\end{format}

%------------------------------------------------------------------------------

%\section{\bf Honors and Awards}
%\begin{itemize}
%% \item College Board National AP Scholar, 2006
%\item FIRST 2006 Las Vegas Regional Champion, FIRST Robotics Competition
%% \item Rachel H. Austin Award, Social Sciences, Palo Alto High School, 2006
%% \item Excellence in Computer Science Award, Mathematics Department, Palo Alto High School, 2004
%\end{itemize}


\section{\bf Computer Skills}
\begin{itemize}
\item Proficiency in software development in C++, Python, Clojure, Javascript, Go, Java
\item Familiarity with Qt, Concurrency, Regular Expressions, Threads, Sockets, SQL, \LaTeX
\item Expert user and administrator of GNU/Linux and Mac OS X
\end{itemize}


%\section{\bf Working Papers}
%
%``The Effects of Ties on Convergence in K-Modes Variants for Clustering
%Categorical Data,''
%with N.\ Orlowski, D.\ Schlorff, D.\ Ca\~{n}as, M.\ T.\ Chu,
%and R.\ E.\ Funderlic (2004).%

%``Updating the Centroid Decomposition with Applications in LSI,''
%with M.\ T.\ Chu, D.\ Ca\~{n}as, R.\ E.\ Funderlic, N.\ Orlowski,
%and D.\ Schlorff (2004).

%``Structural Estimation of Sequential Games of Complete Information'' (2006).

%------------------------------------------------------------------------------

%%===========================================================================%%
% \newpage
% \opening
% 
% \section{\bf Scientific Software}
% 
% Blevins, J., J. Heath, and W. Hereman (2002):
% \href{http://www.mines.edu/fs_home/whereman/software/PDESolutionTester/}
% {\texttt{PDESolutionTester}},
% A Mathematica program for the symbolic verification of exact solutions of
% nonlinear partial differential equations.
% 
% %------------------------------------------------------------------------------
% 
% %\section{\bf Presentations}
% %
% %``Solving Nonlinear Wave Equations with Mathematica,''
% %North Carolina State University, April 23, 2003.
% 
% %---------------------------------------------------------------------------
% 
% \section{\bf Service}
% 
% \begin{itemize}
% \item Vice President, Society of Undergraduate Mathematics, North
%   Carolina State University, 2001--2003
% \item Vice President, Economics Graduate Student Council, Duke
%   University, 2006--2007
% \end{itemize}
% 
% %%---------------------------------------------------------------------------%%
% 
% \section{\bf Honors and Awards}
% \begin{itemize}
% \item \href{http://www.pbk.org/}{Phi Beta Kappa}, 2003
% \item Undergraduate Research Award, North Carolina State University, 2004
% \item Outstanding Teaching Assistant Award, Duke University, 2006
% \end{itemize}
% 
% %%---------------------------------------------------------------------------%%
% 
% \begin{center}
% \vspace{\fill}\ \newline
% {\tiny \rm $ $RCSfile: cv-us.tex,v $ $ }
% {\tiny \rm $ $Date: 2006/12/12 22:53:52 $ $ }
% {\tiny \rm $ $Revision: 1.28 $ $ }
% \end{center}

\end{resume}

\end{document}

%%===========================================================================%%
